As the demand for artificial-intelligence computation continues to grow, photonic neural networks have emerged as a promising route for performing selected linear operations directly in the optical domain. Coherent photonic architectures, which use both the amplitude and phase of light, offer greater computational expressiveness than intensity-only approaches. However, most coherent systems rely on local modulation of both input data and weights on the same chip in order to preserve the stable phase relationships required for interference-based computation. This physical co-location requirement limits the scalability of optical-domain computing and its ability to process remotely sourced data.

This dissertation investigates remote coherent optical computing based on optical injection locking. The proposed approach uses a remotely delivered optical carrier to injection-lock a local semiconductor laser, thereby regenerating a coherent local optical reference without requiring a separate ultra-stable laser, an optical phase-locked loop, or repeated optical-to-electrical and analog-to-digital conversion. The recovered local carrier can then be remodulated and interfered with the original remote signal to perform phase-sensitive optical processing.

The work combines theoretical analysis, numerical simulation, and experimental validation. The theoretical and simulation components examine locking range, injection-ratio dependence, detuning, linewidth-enhancement-factor effects, modulation transfer, and symbol-level multiply-and-accumulate behavior. The experimental components validate injection locking under unmodulated and modulated source conditions, characterize locking stability and sideband dynamics, and establish coherent interference using an injection-locked laser. Together, these results provide design guidance for scalable coherent photonic computing systems that process remotely generated optical data in real time.
